That’s a BigAss Chicken: Care and Managementof Large Chicken Breeds for Optimal Health and Productivity

### 2025-03-01 Manuscript_Final.qmd
Finished data analysis (MM)
corrected title format

---
title:“That’s a BigAss Chicken:  Care and Management of Large Chicken Breeds for Optimal Health and Productivity”
shorttitle: " "That-s-a-BigAss-Chicken"
author:
  - name: Karen Veronica Becerra
    orcid: 0009-0006-4967-0955
    email: kvbecerra@Uchicago.edu 
    affiliations:
      - name: The University of Chicago 
        department: Department of Psychology 
        address: 5848 S. University Avenue
        city: Chicago
        region: IL
        country: USA
        postal-code: 60637
    role:
      - methodology
      - editing
  - name: Kristen M. Johnson
    orcid: 0009-0008-3757-5795
    email: kmjohnson25@uchicago.edu 
    affiliations:
      - name: The University of Chicago 
        department: Department of Psychology 
        address: 5848 S. University Avenue
        city: Chicago
        region: IL
        country: USA
        postal-code: 60637
    role:
      - writing
      - conceptualization
- name: Michael Moroz
    orcid: 0009-0000-9772-0001
    email: mrmoroz@uchicago.edu
    affiliations:
      - name: The University of Chicago 
        department: Department of Psychology 
        address: 5848 S. University Avenue
        city: Chicago
        region: IL
        country: USA
        postal-code: 60637
    role:
      - formal anlaysis
      - visualization

@@

## Finally, plotting the regression

>>>>

---
title: "That’s a BigAss Chicken: Care and Managementof Large Chicken Breeds for Optimal Health and Productivity"
shorttitle: "That-s-a-BigAss-Chicken"
author:
  - name: Karen Veronica Becerra
    orcid: 0009-0006-4967-0955
    email: kvbecerra@Uchicago.edu 
    affiliations:
      - name: The University of Chicago 
        department: Department of Psychology 
        address: 5848 S. University Avenue
        city: Chicago
        region: IL
        country: USA
        postal-code: 60637
    role:
      - methodology
      - editing
  - name: Kristen M. Johnson
    orcid: 0009-0008-3757-5795
    email: kmjohnson25@uchicago.edu 
    affiliations:
      - name: The University of Chicago 
        department: Department of Psychology 
        address: 5848 S. University Avenue
        city: Chicago
        region: IL
        country: USA
        postal-code: 60637
    role:
      - writing
      - conceptualization
- name: Michael Moroz
    orcid: 0009-0000-9772-0001
    email: mrmoroz@uchicago.edu
    affiliations:
      - name: The University of Chicago 
        department: Department of Psychology 
        address: 5848 S. University Avenue
        city: Chicago
        region: IL
        country: USA
        postal-code: 60637
    role:
      - formal anlaysis
      - visualization

@@

## Finally, plotting the regression.
